---
title: "StreetLaw Summary"
author: "Matt Motyl, CivilPolitics.org"
date: "July 15, 2019"
output:
  html_document:
    theme: simplex
    toc: yes
    toc_depth: '4'
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
---
<script>
   $(document).ready(function() {
     $head = $('#header');
     $head.prepend('<center><img src=\"img/cplogo.png\" style=\"width: 500px;\"/></center>')
   });
</script>

<style type="text/css">

body{ /* Normal  */
      font-size: 16px;

h1.title {
  font-size: 34px;
  text-align: center;
}
h4.author { /* Header 4 - and the author and data headers use this too  */
    font-size: 18px;
  text-align: center;
}
h4.date { /* Header 4 - and the author and data headers use this too  */
  font-size: 18px;
  text-align: center;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width=19, fig.height=12)
```

```{r directory, echo=FALSE, warning=FALSE, include=FALSE}
library(data.table)
library(dplyr)
library(tidyr)
library(plotrix)
library(lsr)
library(kableExtra)

# load data
dat<-read.csv("dat/streetlaw.csv")

#drop irrelevant columns
dat1<-dat[,c(7,10:26)]

#rename columns to fit with other analyses in related CP project to enhance comparability across grantees
setnames(dat1,old=c("lastupdated",
                    "om1",
                    "om2",
                    "sl1",
                    "sl2",
                   "sl3",
                   "sl4",
                    "topic",
                   "numcompleted",
                   "teacher",
                    "typedelib",
                    "uniqueid",
                   "pips1",
                    "pips2",
                    "pips3",
                    "pips4",
                   "similar",
                    "pips5"), 
         new=c("lastupdated",
                "disconfirm_like",
                "opinion_question",
                "perspective_gen",
                "perspective_com",
                "others_talk",
                "others_understand",
                "topic",
                "numcompleted",
                "teacher",
                "typedelib",
                "uniqueid",
                "others_good",
                "others_friend",
                "others_smart",
                "others_respect",
                "talk_similar",
                "similar_smart"))
#old.names1<-names(dat)
#new.names1<-paste(old.names1,"_pre", sep="")
#names(dat)<-new.names1



#old.names2<-names(dat2)
#new.names2<-paste(old.names2,"_post", sep = "")
#names(dat2)<-new.names2

#keep.names<-c("lastupdated",
#              "disconfirm_like",
#              "opinion_question",
#              "perspective_gen",
#              "perspective_com",
#              "others_talk",
#              "others_understand",
#              "topic",
#              "numcompleted",
#              "teacher",
#              "typedelib",
#              "uniqueid",
#              "others_good",
#              "others_friend",
#              "others_smart",
#              "others_respect",
#              "talk_similar",
#              "similar_smart")
#
#dat2<-dat1[,keep.names]

# convert unique id to all lower case, remove blank spaces
dat1$uniqueid<-tolower(dat1$uniqueid)
dat1$uniqueid<-gsub(" ", "", dat1$uniqueid, fixed = TRUE)

# identify whether people completed surveys multiple times
repeaters<-as.data.frame(table(dat1$uniqueid))
# check distribution
max(table(repeaters$Freq))
max(repeaters$Freq)
#figure out what that 83 is all about
repeaters[repeaters$Freq==max(repeaters$Freq),]$Var1
# there are 83 instances where participants did not enter an id

repeaters.2<-repeaters[repeaters$Freq==2,]
repeaters.3<-repeaters[repeaters$Freq==3,]

dat1<-dat1[dat1$uniqueid %in% repeaters$Var1,]
#dat<-dat[!dat$topic=="NULL",]
#dat<-dat[!dat$teacher=="NULL",]
#dat<-dat[!dat$typedelib=="NULL",]
#dat$topic[141]
library(dplyr)
library(tidyr)
dat2<-dat1 %>%
  group_by(uniqueid) %>%
  mutate(treatment= ifelse(lastupdated==max(lastupdated), "post","pre"))
dat2$topic<-factor(dat2$topic, levels=c(1,2,3,4,5,6,7,8),
                  labels = c("Compulsory Voting",
                             "Fracking",
                             "Assault Weapons",
                             "Hate Speech",
                             "Immigration",
                             "Juvenile Offense",
                             "Military",
                             "Minimum Wage"))
dat2$teacher<-factor(dat2$teacher,levels=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26), labels =c("Bach","Bergstrom","Betzold","Brown","Bull","Burgett","Christenson","Dittmer","Edson","Goldberg","Hamilton","Howard","Jones-Wagy","Kelly","Livieratos","Lorenz","McVay","Putsche", "Romeyn","Seabreeze","Singhal","Stowe","Toth","Tunning","Vasek","Williams"))

omaha<-c("Betzold", "Dittmer", "Howard", "McKay", "Stowe", "Toth", "Tunning", "Vasek")
dmv<-c("Bach", "Burgett", "Goldberg", "Kelly", "Livieratos", "Romeyn", "Seabreeze", "Singhal", "Williams")
denver<-c("Bergstrom", "Brown", "Bull", "Christenson", "Edson", "Hamilton", "Wagy-Jones", "Lorenz", "Putsche")

locationator<-function(x){ifelse(x %in% omaha==T, "Omaha", ifelse(x %in% dmv==T, "DMV", "Denver"))}
dat2$location<-locationator(dat2$teacher)
dat2$typedelib<-factor(dat2$typedelib, levels = c(1,2,3), labels=c("Community - Student",
                                                                "Community - Nonstudent",
                                                                "Classroom"))
# prep data for analyses comparing locations over time
dat.m<-dat2 %>%
  group_by(treatment, location) %>%
  gather(Question, Score, c(disconfirm_like:others_understand,others_good:similar_smart))
dat.m2<-as.data.frame(dat.m)
dat.m2$Score<-as.numeric(dat.m2$Score)

# prep data for analyses comparing types of deliberation over time
dat.m3<-dat2 %>%
  group_by(treatment, typedelib) %>%
  gather(Question, Score, c(disconfirm_like:others_understand,others_good:similar_smart))
dat.m3<-as.data.frame(dat.m3)
dat.m3$Score<-as.numeric(dat.m3$Score)  

# prep data for analyses comparing topics over time  
dat.m4<-dat2 %>%
  group_by(treatment, topic) %>%
  gather(Question, Score, c(disconfirm_like:others_understand,others_good:similar_smart))
dat.m4<-as.data.frame(dat.m4)
dat.m4$Score<-as.numeric(dat.m4$Score)
dat.m4<-dat.m4[dat.m4$topic=="Compulsory Voting"|dat.m4$topic=="Assault Weapons",]

by.site<-dat.m2 %>%
group_by(Question, location) %>%
do(m_pre=as.numeric(tryCatch(t.test(Score~treatment, data=.)$estimate[2], error=function(e) NA)), m_post=as.numeric(tryCatch(t.test(Score~treatment, data=.)$estimate[1], error=function(e) NA)),
t=as.numeric(tryCatch(t.test(Score~treatment, data=.)$statistic, error=function(e) NA)),
p=as.numeric(tryCatch(t.test(Score~treatment, data=.)$p.value, error=function(e) NA)),
d=as.numeric(tryCatch(cohensD(Score~treatment, data=.), error=function(e) NA)),
se=as.numeric(tryCatch(std.error(.$Score), error=function(e) NA)))
cols.num <- c("m_pre", "m_post","t","d","p", "se")
by.site.nums<-as.data.frame(sapply(by.site[,cols.num], as.numeric))
by.site.names<-as.data.frame(sapply(by.site[,c("location", "Question")], as.character))
by.site.new<-cbind(by.site.nums, by.site.names)


by.community<-dat.m3 %>%
group_by(Question, typedelib) %>%
do(m_pre=as.numeric(tryCatch(t.test(Score~treatment, data=.)$estimate[2], error=function(e) NA)), m_post=as.numeric(tryCatch(t.test(Score~treatment, data=.)$estimate[1], error=function(e) NA)),
t=as.numeric(tryCatch(t.test(Score~treatment, data=.)$statistic, error=function(e) NA)),
p=as.numeric(tryCatch(t.test(Score~treatment, data=.)$p.value, error=function(e) NA)),
d=as.numeric(tryCatch(cohensD(Score~treatment, data=.), error=function(e) NA)),
se=as.numeric(tryCatch(std.error(.$Score), error=function(e) NA)))
cols.num <- c("m_pre", "m_post","t","d","p", "se")
by.community.nums<-as.data.frame(sapply(by.community[,cols.num], as.numeric))
by.community.names<-as.data.frame(sapply(by.community[,c("typedelib", "Question")], as.character))
by.community.new<-cbind(by.community.nums, by.community.names)
library(effsize)

by.topic<-dat.m4 %>%
group_by(Question, topic) %>%
do(m_pre=as.numeric(tryCatch(t.test(Score~treatment, data=.)$estimate[2], error=function(e) NA)), m_post=as.numeric(tryCatch(t.test(Score~treatment, data=.)$estimate[1], error=function(e) NA)),
t=as.numeric(tryCatch(t.test(Score~treatment, data=.)$statistic, error=function(e) NA)),
p=as.numeric(tryCatch(t.test(Score~treatment, data=.)$p.value, error=function(e) NA)),
d=as.numeric(tryCatch(cohensD(Score~treatment, data=.), error=function(e) NA)),
se=as.numeric(tryCatch(std.error(.$Score), error=function(e) NA)))
cols.num <- c("m_pre", "m_post","t","d","p", "se")
by.topic.nums<-as.data.frame(sapply(by.topic[,cols.num], as.numeric))
by.topic.names<-as.data.frame(sapply(by.topic[,c("topic", "Question")], as.character))
by.topic.new<-cbind(by.topic.nums, by.topic.names)

q_levels<-c("others_good",
                    "others_friend",
                    "others_smart",
                    "others_respect",
                    "similar_smart",
                    "talk_similar",
                    "disconfirm_like",
                    "opinion_question",
                    "perspective_gen",
                    "perspective_com",
                   "others_talk",
                   "others_understand")

q_labels<-c("Others are Good",
"Would Friend Others",
"Others are Smart",
"Respect Others",
"Similar Others Smart",
"Like Similarity",
"Like Disconfirming Info",
"Question Beliefs",
"Generation Difference",
"Understand Beliefs",
"Talk to Others",
"Understand Perspective")
library(h2o)
by.site.new$Question<-factor(by.site.new$Question, levels=q_levels, labels=q_labels)
by.community.new$Question<-factor(by.community.new$Question, levels=q_levels, labels=q_labels)
by.topic.new$Question<-factor(by.topic.new$Question, levels=q_levels, labels=q_labels)

### have to make it long here, get the means into one variable
dat.graph<-by.site.new %>%
  group_by(Question, location) %>%
  gather(Treatment, Mean, m_pre:m_post)
### start from here, make graph with stats for each school, before and after ###
dat.graph<-dat.graph[!is.na(dat.graph$Mean),]
dat.graph$Treatment<-factor(dat.graph$Treatment, levels = c("m_pre", "m_post"), labels=c("Before", "After"))

dat.graph.all<-dat.graph %>%
  group_by(Question) %>%
  gather(Treatment, Mean)

```



## Key

Here is the question key containing the exact wording of the question asked in each survey. 

```{r key, echo=FALSE, warning=FALSE}
q_wording<-c("People who hold different views on controversial issues are generally just as good as people who hold similar views as me.", "If I learn that someone holds different controversial views than I do, I become less interested in being friends with him/her.*", "Intelligent people may hold different views from me.", "I respect people who disagree with my views.", "Generally, intelligent people hold similar views as mine.", "I strongly prefer talking with people who share my views on controversial issues than people who do not share my views.", "I like finding out new information that differs what I already think is true.", "I question my own opinions, positions, and viewpoints because they could be wrong.", "People born in a different generation provide important perspectives on controversial topics.", "I feel like I understand better why someone holds different beliefs on the controversial issue after communicating with them.", "I am interested in talking about controversial issues with people who hold different beliefs from me.", "After talking to people with different beliefs on controversial issues, I understand their perspective better.")

key.df<-as.data.frame(q_wording)

rownames(key.df)<-q_labels
names(key.df)<-"Question Wording"
#library(kableExtra)
key.df %>%
  kable(digits=3) %>%
  kable_styling()

```

## Overall Results

To examine whether participants showed improvement from Time 1 to Time 2, I matched their unique id numbers and plotted the mean score for all participants at each time point below. 



```{r plot, echo=FALSE, warning=FALSE}
library(effsize)
by.college.big<-dat.m2 %>%
group_by(Question) %>%
do(m_pre=as.numeric(tryCatch(t.test(Score~treatment, data=.)$estimate[2], error=function(e) NA)), m_post=as.numeric(tryCatch(t.test(Score~treatment, data=.)$estimate[1], error=function(e) NA)),
t=as.numeric(tryCatch(t.test(Score~treatment, data=.)$statistic, error=function(e) NA)),
p=as.numeric(tryCatch(t.test(Score~treatment, data=.)$p.value, error=function(e) NA)),
d=as.numeric(tryCatch(cohensD(Score~treatment, data=.), error=function(e) NA)),
se=as.numeric(tryCatch(std.error(.$Score), error=function(e) NA)))
cols.num <- c("m_pre", "m_post","t","d","p", "se")
by.college.nums<-as.data.frame(sapply(by.college.big[,cols.num], as.numeric))
by.college.names<-as.data.frame(sapply(by.college.big[,c("Question")], as.character))
by.college.newest<-cbind(by.college.nums, by.college.names)
by.college.newest$Question<-factor(by.college.newest$Question, levels=q_levels, labels=q_labels)

dat.graph.all<-by.college.newest %>%
  group_by(Question) %>%
  gather(Treatment, Mean, m_pre:m_post)
dat.graph.all<-dat.graph.all[!is.na(dat.graph.all$Mean),]
dat.graph.all$Treatment<-factor(dat.graph.all$Treatment, levels = c("m_pre", "m_post"), labels=c("Before", "After"))

library(ggplot2)
names1<-c("Others are Good","Would Friend Others", "Others are Smart","Respect Others","Similar Others Smart","Like Similarity")
plot0<-ggplot(dat.graph.all[dat.graph.all$Question %in% names1,], aes(x=Treatment, y=Mean, fill=Treatment)) +
facet_grid(.~Question)+
geom_bar(position=position_dodge(), stat="identity") +
geom_errorbar(aes(ymin=Mean-se, ymax=Mean+se),
width=.2,                    # Width of the error bars
position=position_dodge(.9))+
scale_x_discrete(name="Before or After Event")+
ylab("Score")+
coord_cartesian(ylim = c(1, 100))+
scale_fill_manual(name="Before or After Event", values=c("green4", "purple4"))+
theme(text=element_text(size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 100)) 

plot0

names2<-c("Like Disconfirming Info","Question Beliefs","Generation Difference", "Understand Beliefs","Talk to Others","Understand Perspective")


plot1<-ggplot(dat.graph.all[dat.graph.all$Question %in% names2,], aes(x=Treatment, y=Mean, fill=Treatment)) +
facet_grid(.~Question)+
geom_bar(position=position_dodge(), stat="identity") +
geom_errorbar(aes(ymin=Mean-se, ymax=Mean+se),
width=.2,                    # Width of the error bars
position=position_dodge(.9))+
scale_x_discrete(name="Before or After Event")+
ylab("Score")+
coord_cartesian(ylim = c(1, 100))+
scale_fill_manual(name="Before or After Event", values=c("green4", "purple4"))+
theme(text=element_text(size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 100)) 

plot1

```
<br><br>
Overall, there was a positive effect where participants reported that they would become more interested in being friends with people holding different beliefs on controversial issues from them at time 2 relative to time 1. Unexpectedly, there was a small negative effect where participants reported a decrease in their belief that "People born in a different generation provide important perspectives on controversial topics." Responses to all other questions did not differ between time 1 and time 2.
<br><br>


```{r table, echo=FALSE, warning=FALSE}

by.college.newest$mygroup<-NULL
rownames(by.college.newest)<-by.college.newest$Question
by.college.newest$Question<-NULL
names(by.college.newest)<-c("Pre Score", "Post Score", "T-value", "Effect Size (D)", "P-value", "Standard Error")
by.college.newest$Effect<-ifelse(by.college.newest$`P-value` < .05, "Yes", "No")

library(kableExtra)
by.college.newest %>%
  kable(digits=3) %>%
  kable_styling()
#rownames(dat.jmu)<-dat.jmu$Question
```



## Results by Region {.tabset .tabset-fade}

I broke down the results of each event by location of the event. Each section will be presented: 

- graphically, showing the change in response to each applicable question
- descriptively, showing the means and standard deviations for each question


*Press [Key] to return to the Question Key.

```{r location, echo=F, warning=F}
dat.table<-dat.m %>%
  group_by(Question, location, treatment) %>%
  summarise(n=n())
dat.table$treatment<-factor(dat.table$treatment, levels=c("pre","post"), labels = c("Pre", "Post"))

#dat.table<-dat.table %>%
  #group_by(Question) %>%
  #spread(., location, n)
#dat.table<-dat.table[-4,] # null snuck in

dat.table<-dat.table %>%
  unite(temp, location, treatment) %>%
  spread(temp, n)
dat.table<-dat.table[,c("Question","Denver_Pre", "Denver_Post", "DMV_Pre","DMV_Post","Omaha_Pre", "Omaha_Post")]

#rownames(dat.table)<-dat.table$Question
labels<-c("Like Disconfirming Info",
            "Question Beliefs",
            "Would Friend Others",
            "Others are Good",
            "Respect Others",
            "Others are Smart",
            "Talk to Others",
            "Understand Beliefs",
            "Understand Perspective",
            "Generation Difference",
            "Like Similarity",
            "Similar Others Smart")
rownames(dat.table)<-labels
dat.table$Question<-NULL
names(dat.table)<-c("Denver (Pre)", "Denver (Post)", "DMV (Pre)","DMV (Post)","Number of Omaha (Pre)", "Omaha (Post)")
dat.table<-dat.table[1,c("Denver (Pre)", "Denver (Post)", "DMV (Pre)","DMV (Post)","Number of Omaha (Pre)", "Omaha (Post)")]
dat.table<-t(dat.table)
colnames(dat.table)<-"Surveys Collected"
```

```{r site, echo=FALSE, warning=FALSE}

library(kableExtra)
dat.table %>%
  kable(digits=3) %>%
  kable_styling()
#rownames(dat.jmu)<-dat.jmu$Question
```

### OMAHA
```{r OMAHAlot, echo=FALSE, warning=FALSE}
#### to label our facets ####
dat.graph.omaha<-subset(dat.graph, location=="Omaha")


names1<-c("Others are Good","Would Friend Others", "Others are Smart","Respect Others","Similar Others Smart","Like Similarity")
plot0<-ggplot(dat.graph.omaha[dat.graph.omaha$Question %in% names1,], aes(x=Treatment, y=Mean, fill=Treatment)) +
facet_grid(.~Question)+
geom_bar(position=position_dodge(), stat="identity") +
geom_errorbar(aes(ymin=Mean-se, ymax=Mean+se),
width=.2,                    # Width of the error bars
position=position_dodge(.9))+
scale_x_discrete(name="Before or After Event")+
ylab("Score")+
coord_cartesian(ylim = c(1, 100))+
scale_fill_manual(name="Before or After Event", values=c("green4", "purple4"))+
theme(text=element_text(size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 100)) 

plot0

names2<-c("Like Disconfirming Info","Question Beliefs","Generation Difference", "Understand Beliefs","Talk to Others","Understand Perspective")


plot1<-ggplot(dat.graph.all[dat.graph.all$Question %in% names2,], aes(x=Treatment, y=Mean, fill=Treatment)) +
facet_grid(.~Question)+
geom_bar(position=position_dodge(), stat="identity") +
geom_errorbar(aes(ymin=Mean-se, ymax=Mean+se),
width=.2,                    # Width of the error bars
position=position_dodge(.9))+
scale_x_discrete(name="Before or After Event")+
ylab("Score")+
coord_cartesian(ylim = c(1, 100))+
scale_fill_manual(name="Before or After Event", values=c("green4", "purple4"))+
theme(text=element_text(size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 100)) 

plot1
```

<br><br>
In the Omaha subsample, there was a positive effect where participants reported that they would become more interested in being friends with people holding different beliefs on controversial issues from them at time 2 relative to time 1. Unexpectedly, participants reported that they were less likely to question their own beliefs and respect people with different beliefs. Additionally, participants reported decreased understanding of why people hold different beliefs on controversial issues after communicating with them. Responses to all other questions did not differ between time 1 and time 2.

All summary statistics are included in the table below.  
<br><br>
```{r OMAHAtable, echo=FALSE, warning=FALSE}

dat.omaha<-subset(by.site.new, location=="Omaha")
dat.omaha<-dat.omaha[!is.na(dat.omaha$m_pre),]
dat.omaha$location<-NULL
rownames(dat.omaha)<-dat.omaha$Question
dat.omaha$Question<-NULL
names(dat.omaha)<-c("Pre Score", "Post Score", "T-value", "Effect Size (D)", "P-value", "Standard Error")
dat.omaha$Effect<-ifelse(dat.omaha$`P-value` < .05, "Yes", "No")

library(kableExtra)
dat.omaha %>%
  kable(digits=3) %>%
  kable_styling()
#rownames(dat.jmu)<-dat.jmu$Question
```



### DMV

```{r DMVplot, echo=FALSE, warning=FALSE}
#### to label our facets ####
dat.graph.dmv<-subset(dat.graph, location=="DMV")


names1<-c("Others are Good","Would Friend Others", "Others are Smart","Respect Others","Similar Others Smart","Like Similarity")
plot0<-ggplot(dat.graph.dmv[dat.graph.dmv$Question %in% names1,], aes(x=Treatment, y=Mean, fill=Treatment)) +
facet_grid(.~Question)+
geom_bar(position=position_dodge(), stat="identity") +
geom_errorbar(aes(ymin=Mean-se, ymax=Mean+se),
width=.2,                    # Width of the error bars
position=position_dodge(.9))+
scale_x_discrete(name="Before or After Event")+
ylab("Score")+
coord_cartesian(ylim = c(1, 100))+
scale_fill_manual(name="Before or After Event", values=c("green4", "purple4"))+
theme(text=element_text(size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 100)) 

plot0

names2<-c("Dislike Confirmation","Question Beliefs","Generation Difference", "Understand Beliefs","Talk to Others","Understand Perspective")


plot1<-ggplot(dat.graph.dmv[dat.graph.dmv$Question %in% names2,], aes(x=Treatment, y=Mean, fill=Treatment)) +
facet_grid(.~Question)+
geom_bar(position=position_dodge(), stat="identity") +
geom_errorbar(aes(ymin=Mean-se, ymax=Mean+se),
width=.2,                    # Width of the error bars
position=position_dodge(.9))+
scale_x_discrete(name="Before or After Event")+
ylab("Score")+
coord_cartesian(ylim = c(1, 100))+
scale_fill_manual(name="Before or After Event", values=c("green4", "purple4"))+
theme(text=element_text(size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 100)) 

plot1
```

<br><br>
There were no statistically significant differences from Time 1 to Time 2 on any of the questions in the DMV region.

All summary statistics are included in the table below.
<br><br>

```{r DMVtable, echo=FALSE, warning=FALSE}

dat.dmv<-subset(by.site.new, location=="DMV")
dat.dmv<-dat.dmv[!is.na(dat.dmv$m_pre),]
dat.dmv$location<-NULL
rownames(dat.dmv)<-dat.dmv$Question
dat.dmv$Question<-NULL
names(dat.dmv)<-c("Pre Score", "Post Score", "T-value", "Effect Size (D)", "P-value", "Standard Error")
dat.dmv$Effect<-ifelse(dat.dmv$`P-value` < .05, "Yes", "No")

library(kableExtra)
dat.dmv %>%
  kable(digits=3) %>%
  kable_styling()
#rownames(dat.jmu)<-dat.jmu$Question
```




### DENVER
```{r denplot, echo=FALSE, warning=FALSE}
#### to label our facets ####
dat.graph.denver<-subset(dat.graph, location=="Denver")


names1<-c("Others are Good","Would Friend Others", "Others are Smart","Respect Others","Similar Others Smart","Like Similarity")
plot0<-ggplot(dat.graph.denver[dat.graph.denver$Question %in% names1,], aes(x=Treatment, y=Mean, fill=Treatment)) +
facet_grid(.~Question)+
geom_bar(position=position_dodge(), stat="identity") +
geom_errorbar(aes(ymin=Mean-se, ymax=Mean+se),
width=.2,                    # Width of the error bars
position=position_dodge(.9))+
scale_x_discrete(name="Before or After Event")+
ylab("Score")+
coord_cartesian(ylim = c(1, 100))+
scale_fill_manual(name="Before or After Event", values=c("green4", "purple4"))+
theme(text=element_text(size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 100)) 

plot0

names2<-c("Dislike Confirmation","Question Beliefs","Generation Difference", "Understand Beliefs","Talk to Others","Understand Perspective")


plot1<-ggplot(dat.graph.denver[dat.graph.denver$Question %in% names2,], aes(x=Treatment, y=Mean, fill=Treatment)) +
facet_grid(.~Question)+
geom_bar(position=position_dodge(), stat="identity") +
geom_errorbar(aes(ymin=Mean-se, ymax=Mean+se),
width=.2,                    # Width of the error bars
position=position_dodge(.9))+
scale_x_discrete(name="Before or After Event")+
ylab("Score")+
coord_cartesian(ylim = c(1, 100))+
scale_fill_manual(name="Before or After Event", values=c("green4", "purple4"))+
theme(text=element_text(size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 100)) 

plot1
```

<br><br>
In the Denver subsample, there was a positive effect where participants reported that they would become more interested in being friends with people holding different beliefs on controversial issues from them at time 2 relative to time 1. Unexpectedly, participants reported a slight increase in their liking for communicating with people who hold similar beliefs as them.Responses to all other questions did not differ between time 1 and time 2.

All summary statistics are included in the table below.
<br><br>

```{r dentable, echo=FALSE, warning=FALSE}

dat.denver<-subset(by.site.new, location=="Denver")
dat.denver<-dat.denver[!is.na(dat.denver$m_pre),]
dat.denver$location<-NULL
rownames(dat.denver)<-dat.denver$Question
dat.denver$Question<-NULL
names(dat.denver)<-c("Pre Score", "Post Score", "T-value", "Effect Size (D)", "P-value", "Standard Error")
dat.denver$Effect<-ifelse(dat.denver$`P-value` < .05, "Yes", "No")

library(kableExtra)
dat.denver %>%
  kable(digits=3) %>%
  kable_styling()
#rownames(dat.jmu)<-dat.jmu$Question
```

## Results by Community Level {.tabset .tabset-fade}

I broke down the results of each event by location of the event. Each section will be presented: 

- graphically, showing the change in response to each applicable question
- descriptively, showing the means and standard deviations for each question


*Press [Key] to return to the Question Key.

```{r community, echo=FALSE, warning=FALSE}
dat.graph<-by.community.new %>%
  group_by(Question, typedelib) %>%
  gather(Treatment, Mean, m_pre:m_post)
### start from here, make graph with stats for each school, before and after ###
dat.graph<-dat.graph[!is.na(dat.graph$Mean),]
dat.graph$Treatment<-factor(dat.graph$Treatment, levels = c("m_pre", "m_post"), labels=c("Before", "After"))

dat.graph.all<-dat.graph %>%
  group_by(Question) %>%
  gather(Treatment, Mean)


dat.table<-dat.m3 %>%
  group_by(Question, typedelib, treatment) %>%
  summarise(n=n())
dat.table$treatment<-factor(dat.table$treatment, levels=c("pre","post"), labels = c("Pre", "Post"))

#dat.table<-dat.table %>%
  #group_by(Question) %>%
  #spread(., location, n)
#dat.table<-dat.table[-4,] # null snuck in

dat.table<-dat.table %>%
  unite(temp, typedelib, treatment) %>%
  spread(temp, n)
dat.table<-dat.table[,c("Question","Classroom_Pre", "Classroom_Post", "Community - Nonstudent_Pre","Community - Nonstudent_Post","Community - Student_Pre", "Community - Student_Post")]

#rownames(dat.table)<-dat.table$Question


dat.table$Question<-NULL
names(dat.table)<-c("Classroomn (Pre)", "Classroom (Post)", "Community - Nonstudent (Pre)","Community - Nonstudent (Post)","Community - Student (Pre)", "Community - Student(Post)")
dat.table<-dat.table[1,c("Classroomn (Pre)", "Classroom (Post)", "Community - Nonstudent (Pre)","Community - Nonstudent (Post)","Community - Student (Pre)", "Community - Student(Post)")]
dat.table<-t(dat.table)
colnames(dat.table)<-"Surveys Collected"
```


In the table below we have the number of respondents for which we have pre and post event data by type of sample.

```{r survbreakdown, echo=FALSE, warning=FALSE}

library(kableExtra)
dat.table %>%
  kable(digits=3) %>%
  kable_styling()
#rownames(dat.jmu)<-dat.jmu$Question
```

### CLASSROOM
```{r classplot, echo=FALSE, warning=FALSE}
dat.graph.class<-subset(dat.graph, typedelib=="Classroom")


names1<-c("Others are Good","Would Friend Others", "Others are Smart","Respect Others","Similar Others Smart","Like Similarity")
plot0<-ggplot(dat.graph.class[dat.graph.class$Question %in% names1,], aes(x=Treatment, y=Mean, fill=Treatment)) +
facet_grid(.~Question)+
geom_bar(position=position_dodge(), stat="identity") +
geom_errorbar(aes(ymin=Mean-se, ymax=Mean+se),
width=.2,                    # Width of the error bars
position=position_dodge(.9))+
scale_x_discrete(name="Before or After Event")+
ylab("Score")+
coord_cartesian(ylim = c(1, 100))+
scale_fill_manual(name="Before or After Event", values=c("green4", "purple4"))+
theme(text=element_text(size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 100)) 

plot0

names2<-c("Dislike Confirmation","Question Beliefs","Generation Difference", "Understand Beliefs","Talk to Others","Understand Perspective")


plot1<-ggplot(dat.graph.class[dat.graph.class$Question %in% names2,], aes(x=Treatment, y=Mean, fill=Treatment)) +
facet_grid(.~Question)+
geom_bar(position=position_dodge(), stat="identity") +
geom_errorbar(aes(ymin=Mean-se, ymax=Mean+se),
width=.2,                    # Width of the error bars
position=position_dodge(.9))+
scale_x_discrete(name="Before or After Event")+
ylab("Score")+
coord_cartesian(ylim = c(1, 100))+
scale_fill_manual(name="Before or After Event", values=c("green4", "purple4"))+
theme(text=element_text(size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 100)) 

plot1
```
<br><br>

In the table below, we see that the belief that "people who hold different views on controversial issues are generally just as good as people who hold similar views as me" significantly increased from Time 1 to Time 2. 

In the classroom subsample, there was a positive effect where participants reported that they would become more interested in being friends with people holding different beliefs on controversial issues from them at time 2 relative to time 1. Unexpectedly, participants reported a slight increase in their belief that people who share similar beliefs on controversial issues were smarter than people who held different beliefs on controversial beliefs. Responses to all other questions did not differ between time 1 and time 2.

All summary statistics are included in the table below.
<br><br>

```{r classtable, echo=FALSE, warning=FALSE}

dat.class<-subset(by.community.new, typedelib=="Classroom")
dat.class<-dat.class[!is.na(dat.class$m_pre),]
dat.class$typedelib<-NULL
rownames(dat.class)<-dat.class$Question
dat.class$Question<-NULL
names(dat.class)<-c("Pre Score", "Post Score", "T-value", "Effect Size (D)", "P-value", "Standard Error")
dat.class$Effect<-ifelse(dat.class$`P-value` < .05, "Yes", "No")

library(kableExtra)
dat.class %>%
  kable(digits=3) %>%
  kable_styling()
#rownames(dat.jmu)<-dat.jmu$Question
```

### COMMUNITY - STUDENT
```{r studplot, echo=FALSE, warning=FALSE}
dat.graph.student<-subset(dat.graph, typedelib=="Community - Student")


names1<-c("Others are Good","Would Friend Others", "Others are Smart","Respect Others","Similar Others Smart","Like Similarity")
plot0<-ggplot(dat.graph.student[dat.graph.student$Question %in% names1,], aes(x=Treatment, y=Mean, fill=Treatment)) +
facet_grid(.~Question)+
geom_bar(position=position_dodge(), stat="identity") +
geom_errorbar(aes(ymin=Mean-se, ymax=Mean+se),
width=.2,                    # Width of the error bars
position=position_dodge(.9))+
scale_x_discrete(name="Before or After Event")+
ylab("Score")+
coord_cartesian(ylim = c(1, 100))+
scale_fill_manual(name="Before or After Event", values=c("green4", "purple4"))+
theme(text=element_text(size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 100)) 

plot0

names2<-c("Dislike Confirmation","Question Beliefs","Generation Difference", "Understand Beliefs","Talk to Others","Understand Perspective")


plot1<-ggplot(dat.graph.student[dat.graph.student$Question %in% names2,], aes(x=Treatment, y=Mean, fill=Treatment)) +
facet_grid(.~Question)+
geom_bar(position=position_dodge(), stat="identity") +
geom_errorbar(aes(ymin=Mean-se, ymax=Mean+se),
width=.2,                    # Width of the error bars
position=position_dodge(.9))+
scale_x_discrete(name="Before or After Event")+
ylab("Score")+
coord_cartesian(ylim = c(1, 100))+
scale_fill_manual(name="Before or After Event", values=c("green4", "purple4"))+
theme(text=element_text(size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 100)) 

plot1
```

<br><br>
In the community student subsample, there was a positive effect where participants reported that they would become more interested in being friends with people holding different beliefs on controversial issues from them at time 2 relative to time 1. Unexpectedly, participants reported more aversion to information that challenges their beliefs, a decreased likelihood of questioning their own beliefs, and a decreased perception that communicating with people who hold different beliefs improves their understanding of their beliefs. Responses to all other questions did not differ between time 1 and time 2.

All summary statistics are included in the table below.
<br><br>

```{r studtable, echo=FALSE, warning=FALSE}

dat.student<-subset(by.community.new, typedelib=="Community - Student")
dat.student<-dat.student[!is.na(dat.student$m_pre),]
dat.student$typedelib<-NULL
rownames(dat.student)<-dat.student$Question
dat.student$Question<-NULL
names(dat.student)<-c("Pre Score", "Post Score", "T-value", "Effect Size (D)", "P-value", "Standard Error")
dat.student$Effect<-ifelse(dat.student$`P-value` < .05, "Yes", "No")

library(kableExtra)
dat.student %>%
  kable(digits=3) %>%
  kable_styling()
#rownames(dat.jmu)<-dat.jmu$Question
```

### COMMUNITY - NONSTUDENT
```{r nonsplot, echo=FALSE, warning=FALSE}
dat.graph.non<-subset(dat.graph, typedelib=="Community - Nonstudent")


names1<-c("Others are Good","Would Friend Others", "Others are Smart","Respect Others","Similar Others Smart","Like Similarity")
plot0<-ggplot(dat.graph.non[dat.graph.non$Question %in% names1,], aes(x=Treatment, y=Mean, fill=Treatment)) +
facet_grid(.~Question)+
geom_bar(position=position_dodge(), stat="identity") +
geom_errorbar(aes(ymin=Mean-se, ymax=Mean+se),
width=.2,                    # Width of the error bars
position=position_dodge(.9))+
scale_x_discrete(name="Before or After Event")+
ylab("Score")+
coord_cartesian(ylim = c(1, 100))+
scale_fill_manual(name="Before or After Event", values=c("green4", "purple4"))+
theme(text=element_text(size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 100)) 

plot0

names2<-c("Dislike Confirmation","Question Beliefs","Generation Difference", "Understand Beliefs","Talk to Others","Understand Perspective")


plot1<-ggplot(dat.graph.non[dat.graph.non$Question %in% names2,], aes(x=Treatment, y=Mean, fill=Treatment)) +
facet_grid(.~Question)+
geom_bar(position=position_dodge(), stat="identity") +
geom_errorbar(aes(ymin=Mean-se, ymax=Mean+se),
width=.2,                    # Width of the error bars
position=position_dodge(.9))+
scale_x_discrete(name="Before or After Event")+
ylab("Score")+
coord_cartesian(ylim = c(1, 100))+
scale_fill_manual(name="Before or After Event", values=c("green4", "purple4"))+
theme(text=element_text(size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 100)) 

plot1
```
<br><br>

In the community nonstudent subsample, there were two unexpected, negative effects. First, participants reported liking information than challenges their beliefs less at Time 2 relative to Time 1. Second, participants reported viewing people who held different beliefs as less smart at time 2 relative to time 1.Responses to all other questions did not differ between time 1 and time 2.

All summary statistics are included in the table below.
<br><br>

```{r nonstable, echo=FALSE, warning=FALSE}

dat.non<-subset(by.community.new, typedelib=="Community - Nonstudent")
dat.non<-dat.non[!is.na(dat.non$m_pre),]
dat.non$typedelib<-NULL
rownames(dat.non)<-dat.non$Question
dat.non$Question<-NULL
names(dat.non)<-c("Pre Score", "Post Score", "T-value", "Effect Size (D)", "P-value", "Standard Error")
dat.non$Effect<-ifelse(dat.non$`P-value` < .05, "Yes", "No")

library(kableExtra)
dat.non %>%
  kable(digits=3) %>%
  kable_styling()
#rownames(dat.jmu)<-dat.jmu$Question
```

## Results by Topic {.tabset .tabset-fade}

I broke down the results of each event by location of the event. Each section will be presented: 

- graphically, showing the change in response to each applicable question
- descriptively, showing the means and standard deviations for each question


*Press [Key] to return to the Question Key.

```{r topic,echo=FALSE, warning=FALSE}
dat.graph<-by.topic.new %>%
  group_by(Question, topic) %>%
  gather(Treatment, Mean, m_pre:m_post)
### start from here, make graph with stats for each school, before and after ###
dat.graph<-dat.graph[!is.na(dat.graph$Mean),]
dat.graph$Treatment<-factor(dat.graph$Treatment, levels = c("m_pre", "m_post"), labels=c("Before", "After"))

dat.graph.all<-dat.graph %>%
  group_by(Question) %>%
  gather(Treatment, Mean)


dat.table<-dat.m4 %>%
  group_by(Question, topic, treatment) %>%
  summarise(n=n())
dat.table$treatment<-factor(dat.table$treatment, levels=c("pre","post"), labels = c("Pre", "Post"))

#dat.table<-dat.table %>%
  #group_by(Question) %>%
  #spread(., location, n)
#dat.table<-dat.table[-4,] # null snuck in

dat.table<-dat.table %>%
  unite(temp, topic, treatment) %>%
  spread(temp, n)
dat.table<-dat.table[,c("Question","Assault Weapons_Pre", "Assault Weapons_Post", "Compulsory Voting_Pre","Compulsory Voting_Post")]

#rownames(dat.table)<-dat.table$Question


dat.table$Question<-NULL
names(dat.table)<-c("Assault Weapons (Pre)", "Assault Weapons (Post)", "Compulsory Voting (Pre)","Compulsory Voting (Post)")
dat.table<-dat.table[1,c("Assault Weapons (Pre)", "Assault Weapons (Post)", "Compulsory Voting (Pre)","Compulsory Voting (Post)")]
dat.table<-t(dat.table)
colnames(dat.table)<-"Surveys Collected"
```


In the table below we have the number of respondents for which we have pre and post event data by area.

```{r survbreakdowntopic, echo=FALSE, warning=FALSE}

library(kableExtra)
dat.table %>%
  kable(digits=3) %>%
  kable_styling()
#rownames(dat.jmu)<-dat.jmu$Question
```

### ASSAULT WEAPONS
```{r wepsplot, echo=FALSE, warning=FALSE}
dat.graph.wep<-subset(dat.graph, topic=="Assault Weapons")


names1<-c("Others are Good","Would Friend Others", "Others are Smart","Respect Others","Similar Others Smart","Like Similarity")
plot0<-ggplot(dat.graph.wep[dat.graph.wep$Question %in% names1,], aes(x=Treatment, y=Mean, fill=Treatment)) +
facet_grid(.~Question)+
geom_bar(position=position_dodge(), stat="identity") +
geom_errorbar(aes(ymin=Mean-se, ymax=Mean+se),
width=.2,                    # Width of the error bars
position=position_dodge(.9))+
scale_x_discrete(name="Before or After Event")+
ylab("Score")+
coord_cartesian(ylim = c(1, 100))+
scale_fill_manual(name="Before or After Event", values=c("green4", "purple4"))+
theme(text=element_text(size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 100)) 

plot0

names2<-c("Dislike Confirmation","Question Beliefs","Generation Difference", "Understand Beliefs","Talk to Others","Understand Perspective")


plot1<-ggplot(dat.graph.wep[dat.graph.wep$Question %in% names2,], aes(x=Treatment, y=Mean, fill=Treatment)) +
facet_grid(.~Question)+
geom_bar(position=position_dodge(), stat="identity") +
geom_errorbar(aes(ymin=Mean-se, ymax=Mean+se),
width=.2,                    # Width of the error bars
position=position_dodge(.9))+
scale_x_discrete(name="Before or After Event")+
ylab("Score")+
coord_cartesian(ylim = c(1, 100))+
scale_fill_manual(name="Before or After Event", values=c("green4", "purple4"))+
theme(text=element_text(size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 100)) 

plot1
```
<br><br>

In the assault weapons dialogues, no responses differed between time 1 and time 2.

All summary statistics are included in the table below.
<br><br>

```{r wepstable, echo=FALSE, warning=FALSE}

dat.wep<-subset(by.topic.new, topic=="Assault Weapons")
dat.wep<-dat.wep[!is.na(dat.wep$m_pre),]
dat.wep$topic<-NULL
rownames(dat.wep)<-dat.wep$Question
dat.wep$Question<-NULL
names(dat.wep)<-c("Pre Score", "Post Score", "T-value", "Effect Size (D)", "P-value", "Standard Error")
dat.wep$Effect<-ifelse(dat.wep$`P-value` < .05, "Yes", "No")

library(kableExtra)
dat.wep %>%
  kable(digits=3) %>%
  kable_styling()
#rownames(dat.jmu)<-dat.jmu$Question
```

### COMPULSORY VOTING
```{r voteplot, echo=FALSE, warning=FALSE}
dat.graph.vote<-subset(dat.graph, topic=="Compulsory Voting")


names1<-c("Others are Good","Would Friend Others", "Others are Smart","Respect Others","Similar Others Smart","Like Similarity")
plot0<-ggplot(dat.graph.vote[dat.graph.vote$Question %in% names1,], aes(x=Treatment, y=Mean, fill=Treatment)) +
facet_grid(.~Question)+
geom_bar(position=position_dodge(), stat="identity") +
geom_errorbar(aes(ymin=Mean-se, ymax=Mean+se),
width=.2,                    # Width of the error bars
position=position_dodge(.9))+
scale_x_discrete(name="Before or After Event")+
ylab("Score")+
coord_cartesian(ylim = c(1, 100))+
scale_fill_manual(name="Before or After Event", values=c("green4", "purple4"))+
theme(text=element_text(size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 100)) 

plot0

names2<-c("Dislike Confirmation","Question Beliefs","Generation Difference", "Understand Beliefs","Talk to Others","Understand Perspective")


plot1<-ggplot(dat.graph.vote[dat.graph.vote$Question %in% names2,], aes(x=Treatment, y=Mean, fill=Treatment)) +
facet_grid(.~Question)+
geom_bar(position=position_dodge(), stat="identity") +
geom_errorbar(aes(ymin=Mean-se, ymax=Mean+se),
width=.2,                    # Width of the error bars
position=position_dodge(.9))+
scale_x_discrete(name="Before or After Event")+
ylab("Score")+
coord_cartesian(ylim = c(1, 100))+
scale_fill_manual(name="Before or After Event", values=c("green4", "purple4"))+
theme(text=element_text(size=20), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))+
  scale_y_continuous(expand = c(0, 0), limits = c(0, 100)) 

plot1
```
<br><br>

In the assault weapons dialogues, no responses differed between time 1 and time 2.

All summary statistics are included in the table below.
<br><br>

```{r votetable, echo=FALSE, warning=FALSE}

dat.vote<-subset(by.topic.new, topic=="Compulsory Voting")
dat.vote<-dat.vote[!is.na(dat.vote$m_pre),]
dat.vote$topic<-NULL
rownames(dat.vote)<-dat.wep$Question
dat.vote$Question<-NULL
names(dat.vote)<-c("Pre Score", "Post Score", "T-value", "Effect Size (D)", "P-value", "Standard Error")
dat.vote$Effect<-ifelse(dat.vote$`P-value` < .05, "Yes", "No")

library(kableExtra)
dat.vote %>%
  kable(digits=3) %>%
  kable_styling()
#rownames(dat.jmu)<-dat.jmu$Question
```

